\newpage
\section{Exercises: Complex Algebra}

\begin{enumerate}
  % Exercise 1
  \item Prove $e^{i\pi}+1=0$ using Euler's formula.

  % Exercise 2
  \item Use Euler's formula to write $1/i$ into polar form $Ae^{i\phi}$ with $A,\phi\in\mathbb{R}$.
        What is the phase angle $\phi$?

  % Exercise 3
  \item Show that $i^{i}$ is real-valued using Euler's formula.
        Use Python to calculate this value and verify that it is real.

  % Exercise 4
  \item Use Euler's formula to show that de Moivre's formula is valid for $n\in\mathbb{Z}$:
        \[[\cos(x)+i\sin(x)]^{n}=\cos(nx)+i\sin(nx)\]

  % Exercise 5
  \item Using Euler's formula, it is possible to determine the $n$th root of unity.
        What this means is that we look for all unique values of $z$ which
        satisfy the following equation where $n$ is a positive integer:
        \begin{equation}
          z^{n} = 1.
          \label{ch03:eq_unity}
        \end{equation}
        You probably already know the answer in the case of $n=2$, for which there are two solutions:
        $z_{0}=1$ and $z_{1}=-1$ as both $1^{2}=1$ and $(-1)^{2}=1$. \\
        Provide a general formula that gives $n$ unique values of $z\in\mathbb{C}$ that
        satisfy Equation \ref{ch03:eq_unity}. How many unique solutions of $z$ are there
        for each value of $n$? Hint: remember that $e^{i 2\pi k} = 1$ where
        $k$ is an integer.

  % Exercise 6
  \item Consider the equation $z^{5}=1$, where $z\in\mathbb{C}$.
        \begin{itemize}
          % Exercise 6a)
          \item[a)] Find the five solutions $w_{k}$ for $k=0,1,2,3,4$, to the equation $z^{5}=1$.
          % Exercise 6b)
          \item[b)] Create a Python program to plot the solutions to this equation in the complex plane. Add lines to your plot which connect the point $w_{k}$ to $w_{(k-1)~\mathrm{mod}~5}$. What is the shape drawn?
          % Exercise 6c)
          \item[c)] Add the unit circle to the plot you found in b).
        \end{itemize}

  % Exercise 7
  \item Use the inverse Euler formula to convert $(1-i) e^{-i \omega t} + (1+i) e^{i\omega t}$
        into the following form:
        \begin{equation*}
          A \cos(\omega t  + \phi)
        \end{equation*}
        with $A\in \mathbb{R}$. What is $A$ and what is $\phi$?

  % Exercise 8
  \item Prove, using Euler's formula that:
        \begin{equation*}
          \cos(3\theta) = \cos^3(\theta)-3\cos(\theta)\sin^2(\theta).
        \end{equation*}

  % Exercise 9
  \item Use Euler's formula to prove the following trigonometric identity:
        \begin{align*}
          \cos(\alpha + \beta) & =\cos(\alpha)\cos(\beta) - \sin(\alpha)\sin(\beta)\,\,.
        \end{align*}

  % Exercise 10
  \item Another definition of $e^{z}$ (the complex exponential) is by an extension of the Taylor series
        expansion of $e^{x}$ (the real exponential), as follows
        \[e^{z} := \sum_{k=0}^{\infty}\frac{z^{k}}{k!}, \quad\quad \text{for}\ z\in\mathbb{C}.\]
        That is, $e^{z}$ is taken to mean this infinite series. Use this Taylor series expansion definition to show that:
        \begin{equation}
          e^{i\theta} = \cos(\theta) + i\sin(\theta).
          \label{ch03:euler_formula}
        \end{equation}
        To do this, compute the Taylor series expansion of $e^{i\theta}$.

\end{enumerate}
