% Author: Jørn Olav Jensen

\newpage
\section{Exercises: Ideal and Tapered Filters}

\begin{enumerate}
  % Exercise 1
  \item Define the ideal band-stop filter as: \footnote{That is $\mathcal{H}_{\mathrm{BS}}(\hat{\omega})=1 - \mathcal{H}_{\mathrm{BP}}(\hat{\omega})$.}
        \begin{equation}
          \mathcal{H}_{\mathrm{BS}}(\hat{\omega}) = \left\{ \begin{array}{cc}
            0 & \hat{\omega}_0 < |\hat{\omega}| < \hat{\omega}_1 \\
            1 & \mathrm{otherwise}
          \end{array}\right.\,\,.
        \end{equation}
        Derive the impulse response for the band-stop filter.

  % Exercise 2
  \item Consider the band-stop filter you found in the previous exercise.
        The goal of this exercise is to implement this filter in Python and apply it to filter an audio file.

        \begin{enumerate}[a)]
          % Exercise 2a)
          \item Let $w[n]$ be a tapered window function, like the Hann window of length $N$. Show that the windowed filter can be written as:
                \[ h_{w}[n]=\delta[n-N/2]w[n] + \frac{\sin(\hat{\omega}_{0}(n-N/2))}{(n-N/2)\pi}w[n] - \frac{\sin(\hat{\omega}_{1}(n-N/2))}{(n-N/2)\pi}w[n]. \]

          % Exercise 2b)
          \item Download the \verb|crappy.wav| file from the link:
                \begin{center}
                  \verb|https://bit.ly/3CvE89s|
                \end{center}
                The audio file contains a guitar playing, but it is impossible to hear due to noise.
                Your task is to filter out this noise using a band-stop filter.
                The noise in the signal is contained in a frequency band between $f_{0}=3$ kHz and $f_{1}=5$ kHz,
                but try to experiment with these to see what happens. Implement a band-stop filter using
                Python to remove the noise and recover the original audio. You can use the code shown in Listing \ref{bandex}
                as a starting point.
        \end{enumerate}

        \lstinputlisting[language=Python, caption=Band-stop filter starting point, label=bandex]{ch13/code/ex13_2_precode.py}

\end{enumerate}
